[dcpo_demsupport]

### 2020-08-28 paper/dcpo_demsupport.Rmd
HC_se fixed
adding the apsr fully reproduction, #13

vcovHC_se <-  function(x) {
  plm::vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

@@

estimate_dcpo <- function(aDataset) {

    result_dcpo_1k <- vector(mode = "list")

    result_dcpo_1k[[1]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
    + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1), model = "pooling", data = aDataset)
    result_dcpo_1k[[2]] <- plm(diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1), model = "pooling", data = aDataset)

    result_vars_dcpo_1k <- map(result_dcpo_1k, function(aFit){
      mitools::MIextract(aFit, fun = vcovHC_se)
    })

    result_betas_dcpo_1k <- map(result_dcpo_1k, function(aFit){
      mitools::MIextract(aFit, fun = coef)
    })

  df_result_dcpo <- map2(result_vars_dcpo_1k, result_betas_dcpo_1k, function(aVar, aBeta){
    summary(
      mitools::MIcombine(results = aBeta, variance = aVar)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))
  })
}

df_result_dcpoAPSR <- map(df_dcpo, estimate_dcpo)

>>>>

vcovHC_se <-  function(x) {
  plm::vcovHC(x, method="arellano", cluster="group") %>% 
    diag() %>% 
    sqrt()
}

@@

estimate_dcpo <- vector(mode = "list")

estimate_dcpo[[1]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1)
      + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1),
      model = "pooling",
      data = aDataset
    )
}

estimate_dcpo[[2]] <- function(aDataset) {
  plm(
      diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1) + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1) + diff(cpi_sd, lag = 1) + plm::lag(cpi_sd, 1),
      model = "pooling",
      data = aDataset
    )
}

df_result_dcpoAPSR <- map(estimate_dcpo, function(aModel){
  aFit <- map(df_dcpo, aModel)

  result_vars_dcpo_1k <- mitools::MIextract(aFit, fun = vcovHC_se)
  result_betas_dcpo_1k <- mitools::MIextract(aFit, fun = coef)

  summary(
      mitools::MIcombine(results = result_betas_dcpo_1k, 
                         variance = result_vars_dcpo_1k)
    ) %>% rownames_to_column(var = "term") %>%
    rename(conf.low = `(lower`,
           conf.high = `upper)`,
           estimate = results) %>%
    filter(!str_detect(term, "(Intercept)"))

})
